---
title: "Comparison of Statistical and Machine Learning Models to Predict Insurance Claims for Auto Industry"
author: "Santosh Jnawali, Saron Lemma, and Rafael Pereira"
date: "10/21/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(ggplot2)
library(GGally)
library(greybox)
library(ggcorrplot)
```

#Import Data 
```{r}
Insurance_Claims <- read_csv("insurance_claims.csv")
```

```{r}
#Looking at the dataset 
View(Insurance_Claims)
```


We have 1,0000 Cases(Rows) and 39 Columns
Categorical Columns -
Quantitative Columns  - 

Use spec() look at the column types for the 39 Columns 
```{r}
spec(Insurance_Claims)
```

Making sure the variables are of the appropriate type
```{r}
Insurance_Claims <- read_csv("insurance_claims.csv", 
                             col_types = cols(
                               months_as_customer = col_double(),
                               age = col_double(),
                               policy_number = col_double(),
                               policy_bind_date = col_factor(),
                               policy_state = col_factor(),
                               policy_csl = col_factor(),
                               policy_deductable = col_double(),
                               policy_annual_premium = col_double(),
                               umbrella_limit = col_double(),
                               insured_zip = col_double(),
                               insured_sex = col_factor(),
                               insured_education_level = col_factor(),
                               insured_occupation = col_factor(),
                               insured_hobbies = col_factor(),
                               insured_relationship = col_factor(),
                               `capital-gains` = col_double(),
                               `capital-loss` = col_double(),
                               incident_date = col_factor(),
                               incident_type = col_factor(),
                               collision_type = col_factor(),
                               incident_severity = col_factor(),
                               authorities_contacted = col_factor(),
                               incident_state = col_factor(),
                               incident_city = col_factor(),
                               incident_location = col_factor(),
                               incident_hour_of_the_day = col_double(),
                               number_of_vehicles_involved = col_double(),
                               property_damage = col_factor(),
                               bodily_injuries = col_double(),
                               witnesses = col_double(),
                               police_report_available = col_factor(),
                               total_claim_amount = col_double(),
                               injury_claim = col_double(),
                               property_claim = col_double(),
                               vehicle_claim = col_double(),
                               auto_make = col_factor(),
                               auto_model = col_factor(),
                               auto_year = col_double(),
                               fraud_reported = col_factor()
                             ))
```

# Visualizing missing values 

```{r}
Insurance_Claims
```
Based on the visualization it seems, there are no any missing variables.However, the missing values could be in different forms and character.

# Summary of the dataset 

```{r}
summary(Insurance_Claims)
```


Based on the feature of variables we are removing some of the variables that are very least important to us such as policy_bind_date.

# Looking at the relationship between Response variable and explanatory variables 

[1] "months_as_customer" 
 
```{r}
ggplot(Insurance_Claims)+
  geom_point(aes(x=months_as_customer,y=total_claim_amount))
```
 

[2] "age"  
 
```{r}
ggplot(Insurance_Claims)+
  geom_point(aes(x=age,y=total_claim_amount))
```
 
 
 
 
 
[3] "policy_number"   
 
 

 
 
 
 
 
 
[4] "policy_bind_date"  
 
 
 
 
[5] "policy_state"  
 
```{r}
#frequency plot
ggplot(Insurance_Claims)+     
  geom_bar(aes(x=policy_state))
```
 
 
 
[6] "policy_csl" 



[7] "policy_deductable" 

```{r}
policy_deductible1<- Insurance_Claims %>% 
  group_by(policy_deductable) %>% 
  summarise(total_claim= sum(total_claim_amount))

ggplot(data=policy_deductible1,aes(x=factor(policy_deductable),y=total_claim))+
  geom_col(size=1,color="darkblue",width =.4)

```

```{r}
ggplot(data=Insurance_Claims,aes(x=factor(policy_deductable),y=sum(total_claim_amount)))+
  geom_col(size=1,color="darkblue",width =.4)
```
 
 [8] "policy_annual_premium"  
```{r}
ggplot(Insurance_Claims)+
  geom_point(aes(x=policy_annual_premium,y=total_claim_amount))
```
Based on the visualization variable needs to be binned.  




 [9] "umbrella_limit"    
 
```{r}
ggplot(data=Insurance_Claims,aes(x=factor(umbrella_limit),y=sum(total_claim_amount)))+
  geom_col(size=1,color="darkblue",width =.4)
``` 




[11] "insured_sex"     
```{r}
ggplot(data=Insurance_Claims,aes(x=insured_sex,y=sum(total_claim_amount)))+
  geom_col(size=1,color="darkblue",width =.4)
```
[12] "insured_education_level"    
```{r}
ggplot(data=Insurance_Claims,aes(x=factor(insured_education_level),y=sum(total_claim_amount)))+
  geom_col(size=1,color="darkblue",width =.4)
```
[13] "insured_occupation"       
```{r}
ggplot(data=Insurance_Claims,aes(x=insured_occupation,y=sum(total_claim_amount)))+
  geom_col(size=1,color="darkblue",width =.5)
```
[14] "insured_hobbies"     
```{r}
ggplot(data=Insurance_Claims,aes(x=insured_hobbies,y=sum(total_claim_amount)))+
  geom_col(size=1,color="darkblue",width =.5)
```
[15] "insured_relationship"    
```{r}
ggplot(data=Insurance_Claims,aes(x=insured_relationship,y=sum(total_claim_amount)))+
  geom_col(size=1,color="darkblue",width =.5)
```
[16] "capital-gains"     
```{r}
ggplot(Insurance_Claims)+
  geom_point(aes(x=`capital-gains`,y=total_claim_amount))
```
Needs bining 

[17] "capital-loss"      
```{r}
ggplot(Insurance_Claims)+
  geom_point(aes(x=`capital-loss`,y=total_claim_amount))
```
Needs binning 


[18] "incident_date"     





[19] "incident_type"     
```{r}
ggplot(data=Insurance_Claims,aes(x=incident_type,y=sum(total_claim_amount)))+
  geom_col(size=1,color="darkblue",width =.5)
```
[20] "collision_type"     
```{r}
ggplot(data=Insurance_Claims,aes(x=collision_type,y=sum(total_claim_amount)))+
  geom_col(size=1,color="darkblue",width =.5)
```
[21] "incident_severity"       
```{r}
ggplot(data=Insurance_Claims,aes(x=incident_severity,y=sum(total_claim_amount)))+
  geom_col(size=1,color="darkblue",width =.5)
```
[22] "authorities_contacted"   
```{r}
ggplot(data=Insurance_Claims,aes(x=authorities_contacted,y=sum(total_claim_amount)))+
  geom_col(size=1,color="darkblue",width =.5)
```
[23] "incident_state"         
```{r}
ggplot(data=Insurance_Claims,aes(x=incident_state,y=sum(total_claim_amount)))+
  geom_col(size=1,color="darkblue",width =.5)
```
[24] "incident_city"           
```{r}
ggplot(data=Insurance_Claims,aes(x=incident_city,y=sum(total_claim_amount)))+
  geom_col(size=1,color="darkblue",width =.5)
```
[25] "incident_location"          




[26] "incident_hour_of_the_day"   




[27] "number_of_vehicles_involved"
```{r}
ggplot(data=Insurance_Claims,aes(x=number_of_vehicles_involved,y=sum(total_claim_amount)))+
  geom_col(size=1,color="darkblue",width =.5)
```
[28] "property_damage"   
```{r}
ggplot(data=Insurance_Claims,aes(x=property_damage,y=sum(total_claim_amount)))+
  geom_col(size=1,color="darkblue",width =.5)
```
[29] "bodily_injuries"       
```{r}
ggplot(data=Insurance_Claims,aes(x=bodily_injuries,y=sum(total_claim_amount)))+
  geom_col(size=1,color="darkblue",width =.5)
```
[30] "witnesses"              
```{r}
ggplot(data=Insurance_Claims,aes(x=witnesses,y=sum(total_claim_amount)))+
  geom_col(size=1,color="darkblue",width =.5)
```
[31] "police_report_available"    
```{r}
ggplot(data=Insurance_Claims,aes(x=police_report_available,y=sum(total_claim_amount)))+
  geom_col(size=1,color="darkblue",width =.5)
```

[32] "total_claim_amount"      

Response variable 

[33] "injury_claim"           

[34] "property_claim"      

[35] "vehicle_claim"   




[36] "auto_make"      
```{r}
ggplot(data=Insurance_Claims,aes(x=auto_make,y=sum(total_claim_amount)))+
  geom_col(size=1,color="darkblue",width =.5)
```
[37] "auto_model"      
```{r}
ggplot(data=Insurance_Claims,aes(x=auto_model,y=sum(total_claim_amount)))+
  geom_col(size=1,color="darkblue",width =.5)
```
[38] "auto_year"       
```{r}
ggplot(data=Insurance_Claims,aes(x=auto_year,y=sum(total_claim_amount)))+
  geom_col(size=1,color="darkblue",width =.5)
```
[39] "fraud_reported" 
```{r}
ggplot(data=Insurance_Claims,aes(x=fraud_reported,y=sum(total_claim_amount)))+
  geom_col(size=1,color="darkblue",width =.5)
```

Our dataset has "?" values in the place of missing values, We have to first get rid of those unknown values before we start to create our first models.

# Correlation/Association: 

```{r}
cor_aso_values <- assoc(Insurance_Claims)
value <- as.data.frame(round(cor_aso_values$value,2))
```

```{r,fig.width=20,fig.height=14}
ggcorrplot(value, method = "square")
```


## Binning Variables


## Linear Regression Models
```{r}
lm(total_claim_amount ~ policy_bind_date, data = Insurance_Claims)
```

# looking at the distribution of Total_claim 


```{r}
ggplot(data =Insurance_Claims,aes(x=total_claim_amount))+
  geom_histogram(bins =10,fill="steelblue")+
  xlab("Total_claim")

```

The list of the variables that we don't need: 


policy_number, 
policy_bind_date
policy_csl- because we have other coverage variables that are similar to this
insured_zip
incident date
incident_location -using state and city instead
police report available
injury_claim, property_claim, and vehicle claim- using sum of all as total_claim


## Variables Not Needed for our EDA

The following variables will be dropped and deleted from the data set to make our EDA more straightforward:

policy_number, policy_bind_date, policy_csl - there are other variables, incident_date, 

When we move forward and do the models we need to factor out those variables.
```{r}
Insurance_Claims1 <- subset(Insurance_Claims, select = -c(policy_number, policy_bind_date, policy_csl, insured_zip, incident_date, incident_location, police_report_available, injury_claim, property_claim, vehicle_claim))
Insurance_Claims
```
























